{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-11-25 documents/viscosity.tex
Microfluidic channel

Contrast this with Adair's arguments along the same lines reporting sub-picosecond relaxation times.

However, if we apply the same arguments to microtubules \cite{Viscous2000}, omega_c = 80 GHz, and Q=11.2. Such an effect is so trivial that we find it hard to believe.

>>>>

Contrast this with Adair's arguments along similar lines, but reporting sub-picosecond relaxation times.

However, if we apply the same arguments to microtubules \cite{Viscous2000}, omega_c = 80 GHz, and Q=11.2. The effects of these exposures should have been
